
\documentclass[journal]{IEEEtran}

\usepackage{hyperref}
\usepackage{amssymb}
\usepackage[utf8]{vietnam}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}

\begin{document}

\title{HFCAM-YOLO: A Hardware-Friendly Context-Aware Mamba-YOLO for Real-Time Small Object Detection on UAV Edge Devices}
\author{PHẠM ĐẠI NHÂN - [MSSV]}
\markboth{Trường Đại học Công nghệ thông tin - ĐHQG HCM April 2026 \quad \quad \quad \quad TOTAL: 10 MARKS}{}
\maketitle

\begin{abstract} 
Detecting small objects from Unmanned Aerial Vehicles (UAVs) remains a fundamental challenge due to limited computational resources on edge devices. We propose \textbf{HFCAM-YOLO}, a hardware-friendly architecture specifically designed for the VisDrone benchmark. Our core contribution is the integration of a \textbf{1-bit Multi-Directional Context-Aware Mamba (HFCAM)} block into the YOLOv8 neck. Furthermore, we implement a \textbf{Multi-Directional Scan (V2)} strategy to capture spatial relations from four directions. Results demonstrate that HFCAM-YOLO V2 achieves an \textbf{mAP50 of 32.62\%}, surpassing the baseline YOLOv8n (32.1\%) while being \textbf{3.6x faster} (14.2ms) and reducing parameters by \textbf{16.6\%}.
\end{abstract}

\section{Introduction}
Nowadays, Unmanned Aerial Vehicles (UAVs) have become indispensable in surveillance and traffic monitoring. However, UAV-captured images often feature tiny objects (pedestrians, bicycles, or cars). Existing state-of-the-art detectors like YOLOv8 are computationally expensive. We propose HFCAM-YOLO to achieve a balance between accuracy and efficiency through 1-bit quantization and 4-way spatial scanning.

\section{Materials and Methods}
The HFCAM-YOLO architecture modifies the standard YOLOv8n neck by replacing C2f modules with our proposed \textbf{BiContextMambaBlock}. We use \textbf{1-Bit Binary Quantization} via the Straight-Through Estimator (STE) to convert FLOPs into BOPs. Additionally, our \textbf{Multi-Directional Scan} (V2) strategy processes spatial information along four parallel paths (Forward, Reverse, Vertical, and Vertical-Reverse).

\section{Results}
Testing on VisDrone2019-DET showed that HFCAM-YOLO achieved an \textbf{mAP50 of 32.62\%} and an inference speed of \textbf{14.2ms} (~70 FPS). On Image 711, our model successfully detected \textbf{79 objects}, compared to only 63 by the baseline YOLOv8n.

\section{Conclusion}
HFCAM-YOLO V2 proves that 1-bit quantization combined with multi-directional context scanning is a robust solution for real-time edge processing on UAVs.

\end{document}
